\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-25 doc/flexiblesusy-paper.tex
strted making edits for point 2.  Not finished.

@@

>>>>

The standard input and output of the generated code is given in SLHA
format and an extension of this to incorporate new blocks for models
which go beyond the MSSM and NMSSM. We use the well known SLHAea
\cite{slhaea} to create these SLHA files and the extra blocks may be chosen
by the user. Since the SLHA standard is intended precisely for the
purpose, MSSM and NMSSM codes should be compliant with this, and we
have tested that HDECAY\cite{hdecay} can understand the SLHA output of
FlexibleSUSY.

For models which go beyond this there is no fixed standard for all
names.  Nonetheless extending the SLHA framework and allowing user
control of the new block names should greatly simplify the process of
linking the output to a users own calculator or any new public tools
that are developed for that model.

@@

\bibitem{slhaea} F.S.~Thomas http://fthomas.github.io/slhaea/

\bibitem{hdecay}  A. Djouadi, M. Spira and P.M. Zerwas, Phys. Lett.  B {\bf 264}
(1991) 440 and  Z. Phys. C {\bf 70} (1996) 427;  M. Spira {\it et al.}, Nucl.\
Phys.\ B {\bf 453} (1995) 17;  A.~Djouadi, J.~Kalinowski and M.~Spira, Comput.
Phys. Commun. {\bf 108} (1998) 56; J.~M.~Butterworth, A.~Arbey, L.~Basso, S.~Belov, A.~Bharucha, F.~Braam, A.~Buckley and M.~Campanelli {\it et al.},
  %``The Tools and Monte Carlo working group Summary Report,''
  arXiv:1003.1643 [hep-ph].
